Bayesian analysis of the NESTA study of interventions against  verbal aggression online

### 2021-09-14 bayesianAnalysis/bayesianReport.Rmd
dfirst draft of bayesian analysis done

  return(ggplot(visContrastTreatment, aes(x = CBS, y = contrast, color = group ))+
            geom_pointrange(mapping = 
        aes(ymin = cLow, ymax = cHigh), size = .2, alpha = .5) +theme_tufte())
}

visContrastCBSJoint <- ggarrange(visContrastsCBS(FinalHMC,ADS = -2)+
      ggtitle("ADS=-2")+ylim(c(-2.5,2.5))+ scale_color_discrete(guide=FALSE),
          visContrastsCBS(FinalHMC,ADS = 0)+ggtitle("ADS=0")+
        ylim(c(-2.5,2.5))+ scale_color_discrete(guide=FALSE),
        visContrastsCBS(FinalHMC,ADS = 2)+ggtitle("ADS=2")+
        ylim(c(-2.5,2.5))+ theme(legend.position = c(0.75, 0.1)), ncol = 3)

@@

>>>>

  return(ggplot(visContrastTreatment, aes(x = CBS, y = contrast, color = group ))+
            geom_pointrange(mapping = 
        aes(ymin = cLow, ymax = cHigh), size = .05, 
        fatten = .1, alpha = .5,
        position = position_dodge(width = .8))+
          theme_tufte())
}

visContrastCBSJoint <- ggarrange(visContrastsCBS(FinalHMC,ADS = -2)+
      ggtitle("ADS = -2")+ylim(c(-2.5,2.5))+ scale_color_discrete(guide=FALSE),
          visContrastsCBS(FinalHMC,ADS = 0)+ggtitle("ADS = 0")+
        ylim(c(-2.5,2.5))+ scale_color_discrete(guide=FALSE)+
        removeY,
        visContrastsCBS(FinalHMC,ADS = 2)+ggtitle("ADS = 2")+
        ylim(c(-2.5,2.5))+ theme(legend.position = c(0.75, 0.15))+
        removeY, ncol = 3)

@@

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold",out.width = "100%", warning = FALSE, message = FALSE}

visContrastsADS <- function(model = FinalHMC, CBS = CBS , IC =  5, 
                            ADS = seq(-3,3,by  = 0.1))
{
  data <- expand.grid(CBS, groupID, IC , ADS)
  colnames(data) <- c("CBS", "groupID", "IC", "ADS")
  posterior <- extract.samples(model, n = 1e5)
  mu <- link( model, data=data ) 
  means <-  round(apply(mu , 2 , mean ), 4)
  HPDIs <- round(apply( mu , 2 , HPDI ),4)
  visContrastADS <- cbind(data,means,t(as.data.frame(HPDIs)))

  ones <- 3 * (1:(nrow(visContrastADS)/3))-2
  twos <- 3 * (1:(nrow(visContrastADS)/3))-1
  threes <- 3 * (1:(nrow(visContrastADS)/3))

  colnames(visContrastADS)[c(6,7)] <- c("low", "high")
  contrastADS <- numeric(nrow(visContrastADS))
  for(i in threes){
    contrastADS[i] <- visContrastADS$means[i] - visContrastADS$means[i-2]  
  }
  for(i in twos){
    contrastADS[i] <- visContrastADS$means[i] - visContrastADS$means[i-1]  
  }
  visContrastADS$contrast <- contrastADS
  visContrastADS$shift <-  visContrastADS$contrast - visContrastADS$means
  for(i in ones){
    visContrastADS$shift[i] <- 0
  }
  visContrastADS$cLow <- visContrastADS$low + visContrastADS$shift
  visContrastADS$cHigh <- visContrastADS$high + visContrastADS$shift

  visContrastADS$group = rep(c("control", "empathy", "normative"), 
                             nrow(visContrastADS)/3)
  visContrastTreatmentADS <- visContrastADS[groupID !=1,]

  return(ggplot(visContrastTreatmentADS, aes(x = ADS, y = contrast, color = group ))+
  geom_pointrange(mapping = aes(ymin = cLow, ymax = cHigh), size = .05,
                  fatten = .1, alpha = .5, 
                  position = position_dodge(width = .8)) +theme_tufte())
}

visContrastADSJoint <- ggarrange(visContrastsADS(FinalHMC,CBS = -2)+ggtitle("CBS = -2")
                                 +ylim(c(-2.5,2.5))+ scale_color_discrete(guide=FALSE),
                                 visContrastsADS(FinalHMC,CBS = 0)+ggtitle("CBS = 0")
                                 +ylim(c(-2.5,2.5))+ scale_color_discrete(guide=FALSE)+
                                   removeY,
                                 visContrastsADS(FinalHMC,CBS = 2)+ggtitle("CBS = 2")
                                 +ylim(c(-2.5,2.5))+
                                   theme(legend.position = c(0.75, 0.15))+
                                   removeY, ncol = 3)

visContrastADSJoint2 <- annotate_figure(visContrastADSJoint, 
top = text_grob("(range restricted to (-2.5,2.5), IC at the rounded mean = 5)",
                                                        size = 10))
visContrastADSJoint3 <- annotate_figure(visContrastADSJoint2, 
top = text_grob("Predicted distance from the control group mean vs. ADS (standardized)",
                                                        size = 12))

visContrastADSJoint3
```
\normalsize

Now, let's inspect the impact of intervention counts by treatment type by looking at contrasts (distances from the control group mean) with 89% HPDIs by IC.

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
visContrastsIC <- function(model = FinalHMC, CBS = CBS , IC =  seq(0,30,by = 1), ADS = ADS)
{
  groupID <- 1:3
  data <- expand.grid(CBS, groupID, IC , ADS)
  data
  colnames(data) <- c("CBS", "groupID", "IC", "ADS")
  posterior <- extract.samples(model, n = 1e5)
  mu <- link( model, data=data ) 
  means <-  round(apply(mu , 2 , mean ), 4)
  HPDIs <- round(apply( mu , 2 , HPDI ),4)
  visContrastIC <- cbind(data,means,t(as.data.frame(HPDIs)))

  ones <- 3 * (1:(nrow(visContrastIC)/3))-2
  twos <- 3 * (1:(nrow(visContrastIC)/3))-1
  threes <- 3 * (1:(nrow(visContrastIC)/3))

  colnames(visContrastIC)[c(6,7)] <- c("low", "high")
  contrastIC <- numeric(nrow(visContrastIC))
  for(i in threes){
    contrastIC[i] <- visContrastIC$means[i] - visContrastIC$means[i-2]  
  }
  for(i in twos){
    contrastIC[i] <- visContrastIC$means[i] - visContrastIC$means[i-1]  
  }
  visContrastIC$contrast <- contrastIC
  visContrastIC$shift <-  visContrastIC$contrast - visContrastIC$means
  for(i in ones){
    visContrastIC$shift[i] <- 0
  }
  visContrastIC$cLow <- visContrastIC$low + visContrastIC$shift
  visContrastIC$cHigh <- visContrastIC$high + visContrastIC$shift

  visContrastIC$group = rep(c("control", "empathy", "normative"), nrow(visContrastIC)/3)
  visContrastTreatmentIC <- visContrastIC[groupID !=1,]

  return(ggplot(visContrastTreatmentIC, aes(x = IC, y = contrast, color = group ))+
    geom_pointrange(mapping = aes(ymin = cLow, ymax = cHigh), size = .2, alpha = .5)+
    ylim(c(-2,2)) +theme_tufte())
}

visContrastsICJoint <- ggarrange(
visContrastsIC(ADS = 2, CBS = -2)+removeX+ 
               theme(legend.position = c(0.3, 0.9),
                     legend.key.size = unit(.3, 'cm'),
                     legend.key.height = unit(.3, 'cm'),
                     legend.key.width = unit(.3, 'cm'),
                     legend.title= element_blank())+
  ggtitle("CBS = -2")+
  ylab("ADS = 2"),
    visContrastsIC(ADS = 2, CBS = 0)+removeY+removeX+ scale_color_discrete(guide=FALSE)+
  ggtitle("CBS = 0"),
    visContrastsIC(ADS = 2, CBS = 2)+removeY+removeX+ggtitle("CBS = 2")+ scale_color_discrete(guide=FALSE),
visContrastsIC(ADS = 0, CBS = -2)+removeX+ scale_color_discrete(guide=FALSE)+
  ylab("ADS = 0"),
    visContrastsIC(ADS = 0, CBS = 0)+removeY+removeX+ 
  scale_color_discrete(guide=FALSE),
    visContrastsIC(ADS = 0, CBS = 2)+removeY+removeX+ scale_color_discrete(guide=FALSE),  
visContrastsIC(ADS = -2, CBS = -2)+ scale_color_discrete(guide=FALSE)+
  ylab("ADS = -2"),
    visContrastsIC(ADS = -2, CBS = 0)+removeY+ scale_color_discrete(guide=FALSE),
    visContrastsIC(ADS = -2, CBS = 0)+removeY+ scale_color_discrete(guide=FALSE), 
ncol = 3, nrow = 3
)

visContrastsICJoint2 <- annotate_figure(visContrastsICJoint, 
top = text_grob("(range restricted to (-3,3))", 
                size = 10))
visContrastsICJoint3 <- annotate_figure(visContrastsICJoint2, 
 top = text_grob("Predicted distance from the control group mean vs. IC (standardized)",
                size = 12))

visContrastsICJoint3
```
\normalsize
